Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-01 sattose/paper.tex
:night_with_stars:

\subsubsection{Clone instance contents}\label{chap:clonecontents}
Finally, we looked at the contents of individual clone instances: what combination of declarations and statements they span. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially.
  \item \textbf{Several Methods:} A clone that spans over two or more methods and/or method bodies.
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Includes Fields/Constructor:} A clone that spans a combination of fields/constructors and other things.
  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
\end{enumerate}

>>>>

\subsubsection{Clone instance contents}\label{chap:clonecontents}
Finally, we looked at the contents of individual clone instances: what combination of declarations and statements they span. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item \textbf{Full Method/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans a method partially.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially.
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Includes Fields/Constructor:} A clone that spans fields/constructors, but can also span other statements or declarations.
  \item \textbf{Method/Class/Interface/Enumeration Declaration:} A clone that contains the declaration (usually the first line) of a class, method, interface or enumeration.
\end{enumerate}
